### 2020-09-15 paper/definitions.tex
Progress
Style fixes
Small fixes
Poprawki up to old Ch 1

\TODO{Run proofreader on all text (temporarily disabled because it slowed down IDE)}

We use standard definitions, sourced from the book by \citeauthor{BB98} \citetitle*{BB98}, modified and extended as needed.

\begin{defn}[graph]
  A \emph{graph} $G$ is an ordered pair of disjoint sets $(V, E)$ such that $E$ is the subset of the set $V \choose 2$ that is of unordered pairs of $V$.
\end{defn}

@@

We will only consider finite graphs, that is $V$ and $E$ are always finite. If $G$ is a graph, then $V = V(G)$ is the \emph{vertex set} of $G$, and $E = E(G)$ is the \emph{edge set}. When the context of $G$ is clear we will use $V$ and $E$ to denote its vertex and edge set.

An edge $\{x, y\}$ is said to \emph{join}, or be between vertices $x$ and $y$ and is denoted by $xy$. Thus $xy$ and $yx$ mean the same edge (all our graphs are \emph{undirected}). If $xy \in E(G)$ then $x$ and $y$ are adjacent, connected or neighboring. By $N(x)$ we will denote the \emph{neighborhood} of $x$, that is all vertices $y$ such that $xy$ is an edge. If $xy \notin E(G)$ then $xy$ is a \emph{nonedge} and $x$ and $y$ are \emph{anticonnected}.

\Cref{fig:examplePath} shows an example of a graph $G_0 = (V, E)$ with $V = \{v_1, v_2, v_3, v_4\}$ and $E = \{v_1v_2, v_2v_3, v_3v_4\}$. We will mark edges as solid lines on figures. Nonedges significant to the ongoing reasoning will be marked as dashed lines.

@@

\begin{defn}[path]
  A \emph{path} is a graph $P$ of the form
  \[ V(P) = \{x_1, x_2, \ldots, x_l\},\quad E(P) = \{x_1x_2, x_2x_3, \ldots, x_{l-1}x_l\} \]
\end{defn}
This path $P$ is usually denoted by $x_1x_2\ldots x_l$ or $x_1 - x_2 - \ldots - x_l$. The vertices $x_1$ and $x_l$ are the \emph{endvertices} and ${l-1} = |E(P)|$ is the \emph{length} of the path P. $\{x_2, \ldots x_{l-1}\}$ is the \emph{inside} of the path $P$, denoted as $P^*$.

Graph $G_0$ is a path of length 3, with the inside $G_0^* = \{v_2, v_3\}$. If we would add any edge to $G_0$ it would stop being a path.

@@

Notice, that a cycle is not a path (nor is a path a cycle). If we add an edge $v_1v_4$ to the path $G_0$ it becomes an even cycle $C_4$.

@@

\begin{defn}[complement]
  A \emph{complement} of a graph $G = (V, E)$ is a graph $\overline{G} = (V, {V \choose 2} \setminus E)$, that is two vertices $x, y$ are adjacent in $\overline{G}$ if and only if they are not adjacent in $G$.
\end{defn}

@@

\begin{defn}[anticonnected graph, subset]
  A graph $G$ is anticonnected if $\overline{G}$ is connected.
  A subset $X$ is anticonnected if $\overline{G}[X]$ is connected.
\end{defn}

@@

\begin{defn}[clique]
  A \emph{complete} graph or a \emph{clique} is a graph of the form $G = (V, {V \choose 2})$, that is every two vertices are connected. We will denote a clique on $n$ vertices as $K_n$.
\end{defn}

@@

\begin{defn}[anticlique]
  An \emph{anticlique} is a graph in which there are no edges. We will also call anticliques \emph{independent sets}. 
\end{defn}
In a similar fashion, given a graph $G = (V, E)$, a subset of its vertices $V' \subseteq V$ will be called \emph{independent} (in the context of $G$) if and only if $G[V']$ is an anticlique.

@@

\TODO{Defs below to ch. 1}

>>>>

We begin by recalling the basic notions of graph theory. We use standard definitions, sourced from the book by \citeauthor{BB98} \citetitle*{BB98}, modified and extended as needed.

\begin{defn}[graph]
  A \emph{graph} $G$ is an ordered pair of disjoint sets $(V, E)$ such that $E$ is the subset of the set $V \choose 2$, that is, of unordered pairs of $V$.
\end{defn}

@@

We will only consider finite graphs, that is, $V$ and $E$ are always finite. If $G$ is a graph, then $V = V(G)$ is the \emph{vertex set} of $G$, and $E = E(G)$ is the \emph{edge set}. When the context of $G$ is clear we will use $V$ and $E$ to denote its vertex and edge set.

An edge $\{x, y\}$ is said to \emph{join}, or be between vertices $x$ and $y$ and is denoted by $xy$. Thus $xy$ and $yx$ denote the same edge (all our graphs are \emph{undirected}). If $xy \in E(G)$ then $x$ and $y$ are adjacent, connected or neighboring. By $N(x)$ we will denote the \emph{neighborhood} of $x$, that is, all vertices $y$ such that $xy$ is an edge. Similarly, for $X \subseteq V(G)$, by $N(X)$ we will denote the neighborhood of $X$, meaning all vertices of $v \in V(G) \setminus X$, so that there is a $x \in X$, that $xv$ is an edge in $G$. If $xy \notin E(G)$ then $xy$ is a \emph{nonedge} and $x$ and $y$ are \emph{anticonnected}.

\Cref{fig:examplePath} shows an example graph $G_0 = (V, E)$ with $V = \{v_1, v_2, v_3, v_4\}$ and $E = \{v_1v_2, v_2v_3, v_3v_4\}$. We will mark edges as solid lines on figures. Nonedges significant to the ongoing reasoning will be marked as dashed lines.

@@

For example, for $X = \{v_2\}$, the set $\{v_1, v_3\}$ is $X$-complete in $G$, while the set $\{v_3, v_4\}$ is not.

\begin{defn}[path]
  A \emph{path} is a graph $P$ of the form
  \[ V(P) = \{x_1, x_2, \ldots, x_l\},\quad E(P) = \{x_1x_2, x_2x_3, \ldots, x_{l-1}x_l\} \]
\end{defn}
This path $P$ is usually denoted by $x_1x_2\ldots x_l$ or $x_1 - x_2 - \ldots - x_l$. The vertices $x_1$ and $x_l$ are the \emph{endvertices} and ${l-1} = |E(P)|$ is the \emph{length} of the path P. $\{x_2, \ldots x_{l-1}\}$ is the \emph{inside} of the path $P$, denoted as $P^*$. Notice that we don't allow any edges other than the ones between consecutive vertices for a graph to be called a path.

Graph $G_0$ is a path of length 3, with the inside $G_0^* = \{v_2, v_3\}$. If we  added any edge to $G_0$ it would stop being a path.

@@

Notice that if we add an edge $v_1v_4$ to the path $G_0$ it becomes an even cycle $C_4$.

@@

\begin{defn}[complement]
  A \emph{complement} of a graph $G = (V, E)$ is a graph $\overline{G} = (V, {V \choose 2} \setminus E)$, that is, two vertices $x, y$ are adjacent in $\overline{G}$ if and only if they are not adjacent in $G$.
\end{defn}

@@

\begin{defn}[anticonnected graph, subset]
  A graph $G$ is \emph{anticonnected} if $\overline{G}$ is connected.
  A subset $X$ is \emph{anticonnected} if $\overline{G}[X]$ is connected.
\end{defn}

@@

\begin{defn}[clique]
  A \emph{complete graph} or a \emph{clique} is a graph of the form $G = (V, {V \choose 2})$, that is, every two vertices are connected. We will denote a clique on $n$ vertices as $K_n$.
\end{defn}

@@

\begin{defn}[anticlique]
  An \emph{anticlique} is a graph in which there are no edges. We will also call anticliques \emph{independent sets} or \emph{stable sets}. 
\end{defn}
In a similar fashion, given a graph $G = (V, E)$, a subset of its vertices $V' \subseteq V$ will be called \emph{independent} (in the context of $G$) if and only if $G[V']$ is an anticlique.

@@

\begin{defn}[line graph]
  The \emph{line graph} of a graph $G = (V, E)$ is the graph $L(G)$ with $V(L(G)) = E$ and $E(L(G)) = \{e_1 e_2: e_1, e_2 \in E, e_1 \cap e_2 \neq \emptyset\}$, that is, $e_1, e_2 \in E$ are adjacent if and only if they share an endpoint in $G$.
\end{defn}

### 2020-09-15 paper/experiments.tex
Poprawki up to old Ch 1

Let us describe experiments and their results. All of our algorithms search for an odd hole or an odd antihole and stop when find one, or a evidence of one. Therefore, their running times are greatest with perfect graphs on the input and we decided to use mainly\todo{run some smart nonperfect tests} perfect graphs for our performance benchmarks. For every test, the vertex number were shuffled.

@@

\TODO{split better granulity and detailed}
Split graphs we use are unions of cliques and independent sets of same size, with some edges between them. In generating them, each edge between a vertex from a clique and a vertex from an independent set has had $1/2$ chance to appear.

@@

\TODO{setting $\epsilon = 1/2$ in csdp helped a lot -- how much?}

Calculating $\vartheta(G)$ is the most complicated part of the coloring algorithm. With that done by an external library, the rest of the program is a straightforward implementation of the algorithms in \Cref{sec:coloringEllipsoid}. In most of our tests, the majority of running time was consumed on calculating $\vartheta$ of various graphs. As it was done by an external library, there isn't much optimization potential for us. One thing of note is, that specifying the precision of $\vartheta$ we want to calculate to be $1/3$ sped up the algorithm by TODO. Our main goal of the implementation was to check if this method is still impractical, even on modern equipment. Let us proceed straight to experiments and results.

@@

\begin{figure}
  % \begin{subfigure}{.5\textwidth}
  %   \centering
  %   \input{plots/color.perf.t.in.out.csv.lines.pgf}
  %   \caption{Random perfect graphs}
  % \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.biparite18to48.t.in.out.csv.lines.pgf}
    \caption{Random bipartite graphs}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.perfLin.t.in.out.csv.lines.pgf}
    \caption{Line graphs of random bipartite graphs}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.lattice.t.in.out.csv.lines.pgf}
    \caption{Lattice graphs}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.rook.t.in.out.csv.lines.pgf}
    \caption{Rook graphs}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.knight.t.in.out.csv.lines.pgf}
    \caption{Knight graphs}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering%
    \input{plots/color.hypercube.t.in.out.csv.lines.pgf}
    \caption{Hypercube graphs}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.split.t.in.out.csv.lines.pgf}
    \caption{Split graphs}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.fullBinary.t.in.out.csv.lines.pgf}
    \caption{Full binary trees}
  \end{subfigure}
  \caption{Overall times of CSDP Color}
\end{figure}

\begin{figure}
  \centering
  \input{plots/color.detailed.csv.detailed.pgf}
  \caption{Detailed times of coloring}
\end{figure}

A few things of note. We notice that in rook graphs the graph manipulation other than calculating CSDP takes close to half of overall running time (\cref{plot:colorRookDet}). We didn't particularly optimize this, other than by use of methods developed for Berge graph recognition algorithm. There are surely some optimizations to be made here if need be. Altough, as we can see on other plots, it won't help in majority of the cases.

>>>>

Let us describe experiments and their results. All of our algorithms search for an odd hole or an odd antihole and stop when find one, or a evidence of one. Therefore, their running times are greatest with perfect graphs on the input and we decided to use mainly\todo{run some smart nonperfect tests} perfect graphs for our performance benchmarks. For every test, the vertex number were shuffled. For every randomly generated graph class and for each size, we ran the tests on 10 graphs generated with different seeds and took their average running time.

@@

Split graphs we use are unions of cliques and independent sets of same size, with some edges between them. In generating them, each edge between a vertex from a clique and a vertex from an independent set has had $1/2$ chance to appear.

@@

Calculating $\vartheta(G)$ is the most complicated part of the coloring algorithm. With that done by an external library, the rest of the program is a straightforward implementation of the algorithms in \Cref{sec:coloringEllipsoid}. In most of our tests, the majority of running time was consumed on calculating $\vartheta$ of various graphs. As it was done by an external library, there isn't much optimization potential for us. One thing of note is, that specifying the precision of $\vartheta$ we want to calculate to be $1/3$ sped up the algorithm by TODO. Also, we cache results of calculatin $\vartheta$, meaning that throught whole execution of our coloring algorithm, we only calculate $\vartheta$ for each graph once. Our main goal of the implementation was to check if this method is still impractical, even on modern equipment. Let us proceed straight to experiments and results.

@@

We ran our tests on the data sets generated in the same way as for perfect graph recognition. We only adjusted grah sizes to get the running times of up to a couple of minutes.

First, we present overall running times of the coloring algorithm (\Cref{fig:CSDPLines}) and then breakdown the running time in two parts: calculating $\vartheta$ by the CSDP library and graphs manipulations which constitute the rest of the coloring algorithm (\Cref{fig:CSDPDet}). We note that $\vartheta$ calculation is highly dependent on the type of the graph. For our biggest tested cases of $|V| = 48$, all required calculations of $\vartheta$ take almost 7 minutes in biparite graphs, but only 12 seconds in line graphs of bipartite graphs. Because CSDP library is highly optimized, it is expected that it would run much faster on some graphs. Hovewer, it is not clear what could we do to speedup the running times on tests that CSDP is slow on, such as bipartite graphs of lattice graphs. A potential improvement would be to again use CUDA, this time for $\vartheta$ calculations, possibly utilizing the cuSOLVER library \cite{cusolver}.

We notice that on some graphs, namely line graphs of bipartite graphs, rook graphs and split graphs the time taken by operations other than calculating $\vartheta$ by the CSDP library is quite significant. Hovewer, the overall running times on these graphs are low, so we didn't particularly optimize this, so probably some improvements could be made if need be.

\begin{figure}
  % \begin{subfigure}{.5\textwidth}
  %   \centering
  %   \input{plots/color.perf.t.in.out.csv.lines.pgf}
  %   \caption{Random perfect graphs}
  % \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.biparite18to48.t.in.out.csv.lines.pgf}
    \caption{Random bipartite graphs}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.perfLin.t.in.out.csv.lines.pgf}
    \caption{Line graphs of random bipartite graphs}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.lattice.t.in.out.csv.lines.pgf}
    \caption{Lattice graphs}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.rook.t.in.out.csv.lines.pgf}
    \caption{Rook graphs}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.knight.t.in.out.csv.lines.pgf}
    \caption{Knight graphs}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering%
    \input{plots/color.hypercube.t.in.out.csv.lines.pgf}
    \caption{Hypercube graphs}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.split.t.in.out.csv.lines.pgf}
    \caption{Split graphs}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.fullBinary.t.in.out.csv.lines.pgf}
    \caption{Full binary trees}
  \end{subfigure}
  \caption{Overall times of CSDP Color}
  \label{fig:CSDPLines}
\end{figure}

\begin{figure}
  \centering
  \input{plots/color.detailed.csv.detailed.pgf}
  \caption{Detailed times of coloring}
  \label{fig:CSDPDet}
\end{figure}

### 2020-09-15 paper/implementation.tex
Poprawki up to old Ch 1

First of all, there are many methods for generating all possible paths to choose from. We could simply enumerate all sequences of vertices without repetition and for each one of them check if it is a path (that is if all pairs of vertices next to each other are connected and that there are no other edges), but this would be too slow and render our algorithm unusable.

@@

This simple change in data structure design gave us a speedup of overall running time of our algorithm in the range of 20x\todo{check this}.

Another crucial optimization is to eliminate partial solutions that have edges between not consecutive vertices right away. Also, when we look for an odd hole specifically, we can assume that its first vertex we enumerate is the lowest. Those two optimizations alone make a huge difference. With them, our na\"ive algorithm implementation went from being able to check graphs with $|V|$ up to 12-14, within a couple of minutes, to being faster than CCLSV on most of our tests.

@@

For each path candidate $v$ we call a subroutine $areUnique(v)$ to determine whether all vertices in it are unique. As this subroutine could be called many times for generating a single path, its optimization is very important.

@@

In our use case, a few optimizations can be made. First, we don't need a hashing set. We can have an array of bools, of size $|V(G)|$ and mark vertices of a path there. Paths are usually much shorter than $|V(G)|$, but we operate on small graphs, so we can afford this. Second, we notice that we don't need to create this array for each call of $areUnique$ procedure. Let's instead have a static array $stamp$ of ints and a static $counter$ of how many times we called $areUnique$ method. For each element of a path $v_i$, if the value of $stamp$ array is equal to $counter$ we report that vertices are not unique. Else we set $stamp[v_i] = counter$. When returning from the $areUnique$ method we increment $counter$.

This optimization almost cuts down na\"ive algorithm's running time in half.

@@

\todo{rewrite/rearrange text below}

The Berge recognition algorithm's running time is $O(n^9)$, which brings into question its applicability to any real use case. Although time complexity is indeed a limiting factor, a number of lower level optimizations done on implementation's level (\Cref{sec:Optimizations}) make a very big difference and make it more viable than na\"ive algorithm, at least on some test cases. Also, we explore a new frontier of implementing its most time consuming part on massively parallel GPU architecture, with some good results (\Cref{sec:CUDA}).

\TODO{Anything interesting about algo/data structure?}

@@

Another algorithm for which we found major speedups is the algorithm to generate all possible near-cleaners (\Cref{alg:listNearCleaners}). At its very end, it returns a set that is an union \todo{after rewriting alg, point to a line}. We used a \texttt{dynamic\_bitset} from the boost library \cite{boost} for this purpose. It is a data structure to represent a set of bits, that also allows for fast bitwise operators that one can apply to builtin integers. By using it, the speedup of \Cref{alg:listNearCleaners} was about x. \todo{todo}

After these optimizations, checking each potential near-cleaner (\Cref{alg:testNearCleaner}) is by far the biggest bottlenecks of the CCLSV algorithm. We didn't find any major optimizations there, but \Cref{alg:testNearCleaner} has a good potential for parrallelization, which we explore in \Cref{sec:CUDA}.

@@

In addition to correctness checking, extensive unit test suite allowed us to optimize our algorithm and test different subroutines with ease, without fear of introducing bugs.

@@

Also, we test the algorithm on graphs that we know are perfect -- such as bipartite graphs, line graphs of bipartite graphs and complements thereof. In addition to that, a test on all perfect graphs up to a size of 10\todo{update to 11?} was performed -- we used \cite{graphRepo} as a source of perfect graphs.

@@

In total over 100 \todo{update the munber}cpu-hours of end to end tests were performed without any errors.

@@

CUDA is a parrallel computing platform model created by Nvidia and executed on Nvidia GPUs. It allows to run a program in parallel by many CUDA threads at once. Although usually described by PRAM models, implementing PRAM algorithm in CUDA architecture is not as straightforward as implementing RAM algorith on a cpu. Some of the causes are: synchronization between threads is very costly, there are multiple memory models to choose from, threads run divided in blocks and it is possible to efficiently share memory within blocks and copying memory from and back to CPU suffers from large latency. What is more, there are no standard dynamic structures in PRAM model, let alone CUDA, that are taken for granted in PRAM model, such as hashing maps or sets. We used a library called \emph{moderngpu} for our implementation, because it allows a slightly cleaner code.

\TODO{Implementing get NC is tough -- we rely on set<bitset> to do the work. Maybe we could use a dynamic set from Adam's link? As a "open question"}

@@

Let us recall the \Cref{alg:testNearCleaner}. It calculates array $R$ of shortest paths, then for each 3-vertex path and an additional vertex it does $O(1)$ checks to see if they along with two paths from $R$ give us an odd hole. We will parallelise the work after calculating $R$. Let us notice, that for all $X$s all 3-vertex paths are the same. We calculate them beforehand, then each thread receives a 3-vertex path $x_1 - x_2 - x_3$ and an additional vertex $y_1$ and performs the required checks. This is almost perfect scenario for the GPU -- we do a simple SIMD work in parallel, without a lot scattered memory access.

The part of the CCLSV implemented on the gpu achieved speedup of up to 15x. Which gives us a speedup of up to 9x for overall algorithm.

>>>>

First of all, there are many methods for generating all possible paths to choose from. We could simply enumerate all sequences of vertices without repetition and for each one of them check if it is a path, i.e., if all pairs of vertices next to each other are connected and that there are no other edges, but this would be too slow and render our algorithm unusable.

@@

This simple change in data structure design gave us a speedup of overall running time of our algorithm in the range of about 5x.

Another crucial optimization is to eliminate partial solutions that have edges between not consecutive vertices right away. Also, when we look for an odd hole specifically, we can assume that its first vertex we enumerate is the lowest. Those two optimizations make a huge difference. With them, our na\"ive algorithm implementation went from being able to check graphs with $|V|$ up to 12-14, within a couple of minutes, to being faster than CCLSV on most of our tests.

@@

For each path candidate $v$ we call a subroutine \texttt{areUnique}$(v)$ to determine whether all vertices in it are unique. As this subroutine could be called many times for generating a single path, its optimization is very important.

@@

In our use case, a few optimizations can be made. First, we don't need a hashing set. We can have an array of bools, of size $|V(G)|$ and mark vertices of a path there. Paths are usually much shorter than $|V(G)|$, but we operate on small graphs, so we can afford this. Second, we notice that we don't need to create this array for each call of \texttt{areUnique} procedure. Let's instead have a static array $stamp$ of ints and a static $counter$ of how many times we called \texttt{areUnique} method. For each element of a path $v_i$, if the value of $stamp$ array is equal to $counter$ we report that vertices are not unique. Else we set $stamp[v_i] = counter$. When returning from the \texttt{areUnique} method we increment $counter$.

This optimization alone almost cuts down na\"ive algorithm's running time in half.

@@

The Berge recognition algorithm's running time is $O(n^9)$, which brings into question its applicability to any real use case. Although time complexity is indeed a limiting factor, a number of lower level optimizations done on implementation's level make a very big difference and make it more viable than na\"ive algorithm, at least on some test cases. Also, we explore a new frontier of implementing its most time consuming part on massively parallel GPU architecture, with some good results (\Cref{sec:CUDA}).

@@

% \emergencystretch=10em

Another algorithm for which we found major speedups is the algorithm to generate all possible near-cleaners \Cref{alg:listNearCleaners}). We optimized it by using a a \texttt{dynamic\_bitset} from the boost library \cite{boost}. It is a data structure to represent a set of bits, that also allows for fast bitwise operators that one can apply to builtin integers. At the very end of \Cref{alg:listNearCleaners} a set $\mathcal{R}$ is constructed, which is an union of all possible unions of pairs $X_i$ and $N_j$. We used \texttt{dynamic\_bitset} to represent each of the sets $X_i$ and $N_j$, and the set $\mathcal{R}$. This significantly speeds up the operation of union of two sets (line \ref{line:listNCcalcR}). With this modification, the speedup of \Cref{alg:listNearCleaners} was about 20\%.

After these optimizations, checking each potential near-cleaner by \Cref{alg:testNearCleaner} is by far the biggest bottleneck of the CCLSV algorithm. We didn't find any major optimizations there, but the \Cref{alg:testNearCleaner} has a good potential for parrallelization, which we explore in \Cref{sec:CUDA}.

@@

In addition to correctness checking, extensive unit test suite allowed us to optimize our algorithm and test different subroutines with ease, without the fear of introducing bugs.

@@

Also, we test the algorithm on graphs that we know are perfect -- such as bipartite graphs, line graphs of bipartite graphs and complements thereof. In addition to that, a test on all perfect graphs up to a size of 10 was performed -- we used \cite{graphRepo} as a source of perfect graphs.

@@

In total over 200 cpu-hours of end to end tests were performed without any errors.

@@

CUDA is a parrallel computing platform model created by Nvidia and executed on Nvidia GPUs. It allows to run a program in by many CUDA threads at once. Although usually described by the the PRAM models, implementing PRAM algorithm in CUDA architecture is not as straightforward as implementing a RAM algorith on a cpu. Some of the causes are: synchronization between threads is very costly, there are multiple memory models to choose from, threads run divided in blocks and it is possible to efficiently share memory within blocks and copying memory from and back to CPU suffers from a large latency. What is more, there are no standard dynamic structures in the PRAM model, let alone CUDA, that are taken for granted in the RAM model, such as hashing maps or sets. 
% We used a library called \emph{moderngpu} for our implementation, because it allows a slightly cleaner code.

% \TODO{Implementing get NC is tough -- we rely on set<bitset> to do the work. Maybe we could use a dynamic set from Adam's link? As a "open question"}

@@

Let us recall the \Cref{alg:testNearCleaner}. It calculates array $R$ of shortest paths, then for each 3-vertex path and an additional vertex it does $O(1)$ checks to see if they along with two paths from $R$ give us an odd hole. We will parallelise the work after calculating $R$, that is, lines \ref{line:cudaStart}-\ref{line:cudaEnd} of the \Cref{alg:testNearCleaner}. Let us notice, that for all $X$s all 3-vertex paths enumerated in line \ref{line:3vertex} are the same. We calculate them beforehand, then each CUDA thread receives one 3-vertex path $x_1 - x_2 - x_3$ and an additional vertex $y_1$ and performs the required checks in lines \ref{line:cudaWorkStard}-\ref{line:cudaWorkEnd}. This is almost perfect scenario for the GPU -- we do a simple SIMD work in parallel, without a lot scattered memory access.

The part of the CCLSV implemented on the gpu achieved speedup of up to 15x. Which gives us a speedup of up to 9x for overall CCLSV algorithm.
